The Astropy Project

### 2017-10-31 main.tex
spell out AAS

In the code itself, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated processes procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the AAS.

>>>>

In the code itself, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated processes procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the American Astronomical Society (AAS).
